\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Detecting LLM Authorship}
\date{\today}

\usepackage{xcolor}
\usepackage{pagecolor}
\usepackage{amsthm, amssymb}
\theoremstyle{definition}
\newtheorem*{definition}{Definition}
\usepackage{geometry}
\geometry{legalpaper, margin=1in}




\usepackage{lipsum}  

\usepackage{amsmath}

\usepackage{url}
\usepackage{hyperref}
% \pagecolor{black}
% \color{white}


\begin{document}

\maketitle

\section{Project Description}

Our project has two main goals:

\begin{enumerate}
    \item Given a text document, can we determine if it was human written or LLM generated?
    \item Given a text document that is known to be LLM generated, can we determine which LLM wrote that document?
\end{enumerate}

\noindent The dataset we will use is from the AutoTexTification dataset which can be found \href{https://huggingface.co/datasets/symanto/autextification2023}{here.}

Which contains both human and LLM generated text from 6 different models.

\section{Key Performance Indicators}

There is substantial business value in each of these tasks. For the first task, some possible uses include 
\begin{enumerate}
    \item Monitoring a competitors' business practices by revealing which LLM a rival company may  be using to generate or edit content.
    \item Help detect use of unapproved LLMs, which could pose safety or legal risks (such as if a company allows only locally run LLMs).
    \item Prevent IP contamination, e.g., mixing outputs from proprietary models with open models inappropriately.
    \item As an intermediate input for the second task.

\end{enumerate}

For the second task, some possible uses include 
\begin{enumerate}
    \item Fraud detection, e.g. in user collected survey data
    \item LLM plagiarism detection, as LLM usage can risk reputational harm (e.g. \href{https://www.404media.co/chicago-sun-times-prints-ai-generated-summer-reading-list-with-books-that-dont-exist/}{here})
    \item Academic honesty 
\end{enumerate}

For each of these, the model should not be used as definitive proof of LLM usage, but instead as a way to flag text for further review. 

\end{document}